Constant Error Tolerance Computational Fuzzy Extractors

### 2014-01-24 constantRate/ConstCompFuzzExt.tex
working on second construction

In \apref{sec:conductors}, we show that fuzzy conductors are subject to the same lower bounds on entropy loss as fuzzy extractors.  Instead of using a fuzzy conductor, we define a computational version.  
We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
\label{def:hill ent}
Let $(W, S)$ be a pair of random variables.  $W$ has 
\emph{HILL entropy} at least $k$ conditioned on $S$,
denoted $H^{\hill}_{\epsilon, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon$.
\end{definition}

We now define the two primitives for this approach: a computational fuzzy conductor and a (computational)~randomness extractor.  A computational fuzzy conductor is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
\bnote{depending on what we get from obfuscation may need this to be relaxed HILL entropy.  Would have to redo lemma below, but it is essentially the same.}
\begin{definition}
\label{def:comp fuzzy cond}
Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.  A pair of randomized procedures ``generate'' ($\gen'$) and ``reproduce'' ($\rep'$) is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s_{sec})$-hard with error $\delta$ if $\gen'$ and $\rep'$ satisfy the following properties:
\begin{itemize}
\item The generate procedure $\gen'$ on input $w\in \mathcal{M}$ outputs a string $Y\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure $\rep'$ takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(Y, P)\leftarrow \gen'(w)$, then $\Pr[\rep'( w', P) = Y] \geq 1-\delta$ where the probability is over the randomness of $(\gen', \rep')$.  
If $\dis(w, w') > t$, then no guarantee is provided about the output of $\rep'$.
\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $Y$ has high HILL entropy conditioned on $P$, that is $H^{\hill}_{\epsilon, s_{sec}}(Y |P)\geq \tilde{m}$.
\end{itemize}
\end{definition}

@@

Before describing our construction, we recall the problem we are trying address.  The goal is to derive strong keys from noisy sources.  As discussed in the introduction, our goal is to provide security when $gap = \Hoo(W) - \log|B_t|$ is small or even negative.
In the computational setting once a ``long enough'' key may be expanded using a pseudorandom generator.  Thus, we focus on providing enough security when $gap<0$.  We build a computational fuzzy conductor, noting that it can be converted to a computational fuzzy extractor using \lemref{lem:cond and cext}.%If $gap> \omega(\log n)$~(ignoring losses due to randomness extraction), then a key of any length can be formed by using an information-theoretic fuzzy extractor~(which yields nearly this many bits using an optimal code) and expanding the output with a pseudorandom generator~(or using a secure sketch with a computational extractor).  Using an information-theoretic analysis of a fuzzy extractor this seems to be the best construction possible.  As described in Fuller, Meng, and Reyzin~\cite{fuller2013computational}, use of a computational fuzzy extractor may allow a construction when $gap = O(\log n)$.  Their construction is only applicable for high entropy input and yield a result when $gap$ is small.  We will provide the first construction where $gap$ is negative.

\begin{construction}
\label{cons:first construction}
Let $n$ be a security parameter and let $W = W_1,..., W_\ell$ be a distribution over $\zo^{\ell n}$.  Let $\mathcal{O}$ be a $\ell$-composable obfuscator for the family of point functions over $\zo^n$.  Let $t$ be the desired error-tolerance and let $C\subset \zo^\ell$ %be an output equiprobable 
$(\neigh_t, \epsilon_{code})$-error-correcting code.  
We describe $\gen, \rep$ as follows:

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\ell$
\item Sample $c\leftarrow C, seed\leftarrow \zo^*$.
\item For $i=1,..., \ell$:
\subitem If $c_i = 0$: $p_i = \mathcal{O}(I_{w_i})$.
\subitem If $c_i = 1$: Sample $r_i \leftarrow U_n$. 
\subsubitem Let $p_i = \mathcal{O}(I_{r_i})$.
\item Output $(c, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p)$ 
\item For $i=1,..., \ell$:
\subitem If $p_i(w_i') = 1$ set $c_i' = 0$.
\subitem Else set $c_i' = 1$.
\item Set $c = \decode(c')$.
\item Output $c$.
\end{enumerate}
\vspace{0.15in}
\end{minipage} 
\end{tabular}
\end{center}
\label{cons:informal construction}
\end{construction}

@@

\subsection{Security of Construction}
\label{sec:sec of construction}
Assuming virtual black-box obfuscation, we argue security in the presence of equality oracles for each block.  The adversary is provided with equality oracles for each block individually.  Security rests on an adversary's inability to tell whether they are working with obfuscations of $w_i$ or random points using \emph{adaptive} equality queries.  Our construction is secure as long as enough blocks are unpredictable after adaptive queries:

\begin{definition}
\label{def:block guessable}
Let $\mathcal{O}_{w_1,..., w_\ell}$ be an oracle that return $\mathcal{O}_{w_1,..., w_\ell}(i, w_i')=\left( w_i\overset{?}=w_i'\right)$.
A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if for any adversary $A$~(not bounded in time or space) with oracle access to $\mathcal{O}$ making at most $q$ queries there exists a set $\mathcal{I}$ of size at least $\ell -\beta$ such that 
\[
\forall i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))\geq \alpha.
\]
\end{definition}

\noindent We argue security assuming that the adversary knows the value of all blocks outside of $\mathcal{I}$.  The outline of the proof is to:

\begin{itemize}
\item Show that conditioned on the values of all other indices, $\mathcal{I}^c$, $C$ still has many possible values.  That is, $\Hav(C | C_{\mathcal{I}^c})$ is large~(\clref{cl:many locations ent}).
\item Assume that the adversary has perfect knowledge of $C_{\mathcal{I}^c}$.
\item For all codewords $c, c' \in C| C_{\mathcal{I}^c}$, the codewords $c, c'$ are indistinguishable given the adversary's view~(\lemref{lem:codewords in I close}).
%\item The distribution $ C| C_{\mathcal{I}^c} \wedge View(A)$ is close to $C| C_{\mathcal{I}^c}$.  
%\item For all indices in $\mathcal{I}$, the adversary's guess for $c_i, i\in \mathcal{I}$ is close to the prior distribution $C_i | C_{\mathcal{I}^c}$.  
%\item Without seeing a $1$ on a particular block, it is impossible to the distinguish between $c_i=1$ and $c_i=0$.  
%tell if a $1$ or $0$ On all blocks where the probability of a query having returned a $1$ is negligible, it is impossible to tell if you presented with an obfuscation of $W_i$ or a uniform random variable.
% $c_i, i\not \in \mathcal{I}$ there are many possible values of $c\in C$~(\clref{cl:many locations ent}).
%\item Any two codewords, $c_1, c_2\in C | C_{\mathcal{I}^c}$ are statistically close given the adversary's view.
\item The set of codewords $C| View(A) \wedge C_{\mathcal{I}^c}$ has conditional min-entropy~(and thus $C|View(A)$ has conditional min-entropy)~(\corref{cor:avg min after view}).  
\item By the security of obfuscation for every adversary $A$, there exists a simulator $S$ such that $C | A^{P_1,..., P_\ell}$ is computationally indistinguishable from $C | S^{\mathcal{O}}$%~(\lemref{lem:obf has hill ent}).
\bnote{I am having a little trouble formalizing this.  Was hoping for HILL entropy but I don't think that's true.  Will we get relaxed HILL entropy?}
\end{itemize}

Let $\mathcal{I}$ be the set of all indices in \defref{def:block guessable}.  Then $\Hav(C | C_{\mathcal{I}^c}) \geq |C| - \beta$~(by \clref{cl:many locations ent}).  We now show that codewords differing in positions of $\mathcal{I}$ are indistinguishable.
\begin{lemma}
\label{lem:codewords in I close}
Let $c_1, c_2$ be two codewords that agree on all indices $\mathcal{I}^c$.  Then, 
\[
\Delta( ((View(A), C_{\mathcal{I}^c} )| C = c_1),( (View(A), C_{\mathcal{I}^c})  | C= c_2)) < 2^{\alpha+1}.
\]
\end{lemma}
\begin{proof}
Recall that for all $i\in \mathcal{I}$, $\Hav(W_i | View(A))\geq \alpha$.  The only information about $C_i$ is contained in the query responses.  Thus, it suffices to show that whether $c_i= 1$ or $c_i=0$, with probability $1-2^{-\alpha+1}$ all responses to $c_i$ are $0$.  Suppose not, that is suppose, the probability of a nonzero response on an $i$ query is $>2^{-\alpha+1}$.  Since $w, w'$ are independent of $p$, the probability of this happening when $c_i = 1$ is at most $q/2^n$.  Thus, it must occur with probability:
\begin{align*}
2^{-\alpha+1}&>\Pr[\text{non zero response location }i]\\
\Pr[\text{non zero response location }i] &= \Pr[c_i =1]\Pr[\text{non zero response location }i\wedge c_i=1] \\&+ \Pr[c_i=0] \Pr[\text{non zero response location }i \wedge c_i=0]\\
&=1/2 \times 2^{-n+\log q} + 1/2 \Pr[\text{non zero response location }i \wedge c_i=0]
\end{align*}
We now show that $n-\log q \geq \alpha$:
\begin{claim}
$n-\log q \geq \alpha$
\end{claim}
\begin{proof}
Consider one particular $i \in \mathcal{I}$.  It suffices to show that there exists an adversary $A$ making $q$ queries such that the remaining entropy in that block is at most $n-\log (q+1)$.  Let $W_i$ be a distribution, consider $A$ that asks the $q$ most likely outcomes, the total probability of this block must be at least $2^{-n+\log q}$.  After these queries, Then, the remaining min-entropy is at most:
\begin{align*}
\Hav(W_i | View(A)) &\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1+ \Pr[\text{no }q_i=1]\times \Pr[\text{most likely outcome}|q_1,...,q_q]\right)\\
&\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1\right)\\
&=-\log\left( 2^{-n+\log q} \right) = n-\log q
\end{align*}
\end{proof}

We then have that:
\begin{align*}
 \Pr[\text{non zero response location }i \wedge c_i=0] &> 2(2^{-\alpha} - 2^{-(n+1) +\log q} )\\
 &\geq 2\times 2^{-\alpha-1}  = 2^{-\alpha}
 \end{align*}
 When there is a $1$ response and $c_i=0$ this means that there is no remaining min-entropy.  If this occurs with over $2^{-\alpha}$ probability this violates the super-logarithmic conditional min-entropy condition.  Thus, for all $c_1, c_2\in C| C_{\mathcal{I}^c}$ the statistical distance is at most $2^{-\alpha+1}$.
\end{proof}

%\begin{lemma}
%\bnote{what goes here?}
%Let $\mathcal{I}$ be a set of indices such that for all $i\in \mathcal{I}$, $\Hav(W_i | View(A))$
%\end{lemma}
%\begin{lemma}
%\label{lem:super log indist by equal queries}
%Let $W$ and $U$ be two distributions of super-logarithmic entropy.  Then for all adversaries $A$, $q = poly(n)$ queries, $\Delta(View(A^{\mathcal{O}_W(\cdot)}), View(A^{\mathcal{O}_U(\cdot)}))\leq \ngl(n)$.
%\end{lemma}
%\begin{proof}
%It suffices to show that with the probability of all responses being $0$ is overwhelming.  Clearly, in the case when all responses are $0$ the views are identical, and thus the statistical distance is $0$.  \bnote{Finish this proof}
%\end{proof}

%\begin{lemma}
%\label{lem:code bits statistically indist}
%Let $X_i = W_i$ if $c_i = 1$, otherwise let $X_i = U$.  Then, for every $i$, $\Delta(View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})| c_i = 1, View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)} | c_i =0) \leq \ngl(n)$.
%\end{lemma}
%\begin{proof}
%\bnote{Do this}
%\end{proof}
%We can extend this lemma to the entire codeword $C$:
%\begin{lemma}
%For all $c_1, c_2 \in C$ we have the following: 
%\[
%\Delta(View(A^{\mathcal{O}_{(X_{c_{1_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)})| C = c_1, View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}(\cdot, \cdot)} | C = c_2)) \leq \ngl(n).
%\]
%\end{lemma}
The prior lemma implies that the $View$ does not increase the probability of any codeword by much.
\begin{lemma}
\label{lem:no codeword high prob}
For all $c\in C|C_{\mathcal{I}^c}$, 
\[
\expe_{View(A)} \Pr[C=c | C_{\mathcal{I}^c} \wedge View(A)] \leq \Pr[C=c | C_{\mathcal{I}^c}]+2^{-(\alpha-1)}.
\]
\end{lemma}
\begin{proof}
We begin by noting there must exist some $c\in C|C_{\mathcal{I}^c}$ such that 
\[
\expe_{view\leftarrow View}\Pr[C = c | C_{\mathcal{I}^c}] \le \frac{1}{| C| C_{\mathcal{I}^c}|}.
\]
Otherwise the sum of the probabilities of $c\in C | C_{\mathcal{I}^c}$ will be greater than $1$.  Let $c_{min}$ be one such value.
Let $c^*$ be an arbitrary $c^*$ in the support of $C|C_{\mathcal{I}^c}$.  Suppose that  
\begin{align*}
\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C=c^* | C_{\mathcal{I}^c} \wedge view ] &\geq \Pr[C=c^* | C_{\mathcal{I}^c} ]+ 2^{-(\alpha-1)} \\
\end{align*}
This means that the difference between the expected probability of $c_{min}$ and $c^*$ is at least $2^{-\alpha+1}$.  Thus, there is an unbounded distinguisher that can tell between the two cases, violating the statistical distance property of   \lemref{lem:codewords in I close}.  This is a contradiction and completes the proof.
\end{proof}
\begin{corollary}
\label{cor:avg min after view}
$\Hav(C| View(A))\geq \Hav(C | View (A) \wedge C_{\mathcal{I}^c}) \geq \min \{ \Hav(C | C_{\mathcal{I}^c}), \alpha-1\} -1= \min\{ |C| - |\mathcal{I}^c|, \alpha-1\} -1$.
\end{corollary}
\begin{proof}
%Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$). 
Taking the negative log of \lemref{lem:no codeword high prob} one has:
\begin{align*}
\Hav(C_i |  View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot)}))
 &= \\
 -\log \left(\expe_{view \leftarrow View}\max_{c\in C|C_{\mathcal{I}^c}}\Pr[C =c | view \wedge C_{\mathcal{I}^c} ]  \right) &\geq -\log (\Pr[C=c^* | C_{\mathcal{I}^c} ]+ 2^{-\alpha+1}) \\
 &\geq \min \{-\log P_c, -\log 2^{-\alpha+1}\} -1\\
 &= \min \{ \Hav(C | C_{\mathcal{I}^c}), \alpha-1\}-1 
\end{align*}
\end{proof}
%\begin{lemma}
%\label{lem:obf has hill ent}
%For every $s_{sec} = \poly(n)$, there exists some $\epsilon = \ngl(n)$ such that $H^{\hillrlx}_{\epsilon, s_{sec}}(C | P) \geq |C| - \ngl(n)$.
%\end{lemma}
%\begin{proof}
%Suppose not, that is for all $\Hav( X | Y) \geq |C| - \ngl(n)$ there exists some $D$ of size $s_{sec} = \poly(n)$ and $\epsilon = 1/\poly(n)$ such that $\Pr[D(C, P) = 1] - \Pr[D(X, Y)  = 1] = \epsilon$.  Let $ (X, Y)  = (C, 
%\end{proof}
%By similar reasoning we can extend this lemma to the entire codeword:
%\begin{lemma}
%If $C$ is output equiprobable then, $\Hav(C | View(A^{\mathcal{O}_{(X_{c_{2_1}},..., X_{c_{2_\ell}})}})) \geq |C| - \ngl(n)$.
%\end{lemma}
%\begin{lemma}
%$\Hoo(C | View (A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot, \cdot)})) \geq \log |C| - o(\ell \log n)$.
%\end{lemma}

@@

We now show that there must be a super-logarithmic jump early enough.

>>>>

In \apref{sec:conductors}, we show that fuzzy conductors are subject to the same lower bounds on entropy loss as fuzzy extractors.  To overcome these bounds, we use a computational version of a fuzzy conductor.  
We use the common notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
\label{def:hill ent}
Let $(W, S)$ be a pair of random variables.  $W$ has 
\emph{HILL entropy} at least $k$ conditioned on $S$,
denoted $H^{\hill}_{\epsilon, s_{sec}}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, S),(X,S))\leq \epsilon$.
\end{definition}

We now define the two primitives for this approach: a computational fuzzy conductor and a (computational)~randomness extractor.  A computational fuzzy conductor is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
\begin{definition}
\label{def:comp fuzzy cond}
Let $\mathcal{W}$ be a family of probability distributions over $\mathcal{M}$.  A pair of randomized procedures ``generate'' ($\gen'$) and ``reproduce'' ($\rep'$) is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s_{sec})$-hard with error $\delta$ if $\gen'$ and $\rep'$ satisfy the following properties:
\begin{itemize}
\item The generate procedure $\gen'$ on input $w\in \mathcal{M}$ outputs a string $Y\in\{0,1\}^\ell$ and a helper string $P\in\{0,1\}^*$.
\item The reproduction procedure $\rep'$ takes an element $w'\in\mathcal{M}$ and a bit string $P\in\{0,1\}^*$ as inputs.  The \emph{correctness} property guarantees that if $\dis(w, w')\leq t$ and $(Y, P)\leftarrow \gen'(w)$, then $\Pr[\rep'( w', P) = Y] \geq 1-\delta$ where the probability is over the randomness of $(\gen', \rep')$.  
If $\dis(w, w') > t$, then no guarantee is provided about the output of $\rep'$.
\item The \emph{security} property guarantees that for any distribution $W\in \mathcal{W}$, the string $Y$ has high HILL entropy conditioned on $P$, that is $H^{\hill}_{\epsilon, s_{sec}}(Y |P)\geq \tilde{m}$.
\end{itemize}
\end{definition}

@@

Before describing our construction, we recall the problem we are trying address.  The goal is to derive strong keys from noisy sources.  As discussed in the introduction, our goal is to provide security when $gap = \Hoo(W) - \log|B_t|$ is small or even negative.
In the computational setting once a ``long enough'' key may be expanded using a pseudorandom generator.  Thus, we focus on providing enough security when $gap<0$.  We build a computational fuzzy conductor, which can be converted to a computational fuzzy extractor using a computational extractor~(\lemref{lem:cond and cext}).%If $gap> \omega(\log n)$~(ignoring losses due to randomness extraction), then a key of any length can be formed by using an information-theoretic fuzzy extractor~(which yields nearly this many bits using an optimal code) and expanding the output with a pseudorandom generator~(or using a secure sketch with a computational extractor).  Using an information-theoretic analysis of a fuzzy extractor this seems to be the best construction possible.  As described in Fuller, Meng, and Reyzin~\cite{fuller2013computational}, use of a computational fuzzy extractor may allow a construction when $gap = O(\log n)$.  Their construction is only applicable for high entropy input and yield a result when $gap$ is small.  We will provide the first construction where $gap$ is negative.

\begin{construction}
\label{cons:first construction}
Let $n$ be a security parameter and let $W = W_1,..., W_\ell$ be a distribution over $\zo^{\ell n}$.  Let $\mathcal{O}$ be a $\ell$-composable obfuscator for the family of point functions over $\zo^n$.  Let $t$ be the desired error-tolerance and let $C\subset \zo^\ell$ be a
$(\neigh_t, \epsilon_{code})$-error-correcting code.  
We describe $\gen, \rep$ as follows:

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\ell$
\item Sample $c\leftarrow C$.
\item For $i=1,..., \ell$:
\subitem If $c_i = 0$: $p_i = \mathcal{O}(I_{w_i})$.
\subitem Else: Sample $r_i \leftarrow U_n$. 
\subsubitem Let $p_i = \mathcal{O}(I_{r_i})$.
\item Output $(c, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p)$ 
\item For $i=1,..., \ell$:
\subitem If $p_i(w_i') = 1$: set $c_i' = 0$.
\subitem Else: set $c_i' = 1$.
\item Set $c = \decode(c')$.
\item Output $c$.
\end{enumerate}
\vspace{0.15in}
\end{minipage} 
\end{tabular}
\end{center}
\end{construction}

@@

\subsection{Security of Construction}
\label{sec:sec of construction}
\bnote{this paragraph needs to be rewritten}
Assuming virtual black-box obfuscation, we argue security in the presence of equality oracles for each block.  The adversary is provided with equality oracles for each block individually.  Security rests on an adversary's inability to tell whether they are working with obfuscations of $w_i$ or random points using \emph{adaptive} equality queries.  Our construction is secure as long as enough blocks are unpredictable after adaptive queries:

\begin{definition}
\label{def:block guessable}
Let $\mathcal{O}_{w_1,..., w_\ell}$ be an oracle that returns \[\mathcal{O}_{w_1,..., w_\ell}(i, w_i')=
\begin{cases}
1 & w_i = w_i'\\
0 & \text{otherwise}.
\end{cases}
\]
A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if for any unbounded adversary $A$ with oracle access to $\mathcal{O}$ making at most $q$ queries there exists a set $\mathcal{I}\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that 
\[
\forall i\in \mathcal{I}, \Hav(W_i |View(A^{\mathcal{O}_{W}(\cdot, \cdot)}))\geq \alpha.
\]
\end{definition}

%\noindent We argue security assuming that the adversary knows the value of all blocks outside of $\mathcal{I}$.  
We show security of \consref{cons:first construction} for distributions satisfying \defref{def:block guessable}.
To show security it is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$ are indistinguishable.  Let $\mathcal{I}$ be the set of indices that exists in \defref{def:block guessable}, the distribution $C'$ is defined as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $\mathcal{I}$.  First note that $\Hav(C' |P) =\Hav(C' | C_{\mathcal{I}^c} = C'_{\mathcal{I}^c}) = |C| - |\mathcal{I}^c|$~(\clref{cl:many locations ent}).  It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))$.  
Define the distribution $X$ as follows:
\[X_i = 
\begin{cases}
W_i & C_i = 0\\
R_i & C_i = 1.
\end{cases}\]
The outline for the rest of the proof is as follows:
\begin{itemize}
\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$, since $P$ is a collection of obfuscated programs there exists a simulator, $S$~(outputting a single bit), such that $D(C, P) \approx_c S^{\mathcal{O}_X(\cdot, \cdot)}(C)$~(\defref{def:obf}).
\item Show that even an unbounded $S$ with oracle access to $X_1,..., X_\ell$ cannot distinguish between $C$ and $C'$.  That is, $S^{\mathcal{O}_X(\cdot, \cdot)}(C) \approx S^{\mathcal{O}_X(\cdot, \cdot)}(C')$.
This is done in \lemref{lem:sim cannot distinguish}.
% the following steps:
%\begin{itemize}
%%\item Show that conditioned on the values of all other indices, $\mathcal{I}^c$, $C$ still has many possible values.  That is, $\Hav(C | C_{\mathcal{I}^c})$ is large~(\clref{cl:many locations ent}).
%%\item Assume that the simulator has knowledge of $C_{\mathcal{I}^c}$.
%\item For all codewords $c, c' \in C| C_{\mathcal{I}^c}$, the codewords $c, c'$ are indistinguishable given the simulator's view~(\lemref{lem:codewords in I close}).
%\item The two distributions $C$ and $C'$ are indistinguishable given the simulator's view~(\bnote{this needs to be written down.})
%\item The set of codewords $C| View(S) \wedge C_{\mathcal{I}^c}$ has conditional min-entropy~(and thus $C|View(S)$ has conditional min-entropy)~(\corref{cor:avg min after view}).  
%\item Any adversary given $C$ or a fresh $C'$ cannot statistically distinguish.
%\end{itemize}
\item By the security of obfuscation, $S^{\mathcal{O}}(C') \approx_c D(C', P)$~(\defref{def:obf}).
\end{itemize}

Together these arguments allow us to conclude:
\begin{theorem}
\label{thm:security of cons}
Let $\mathcal{O}$ be an $\ell$-composable virtual black box obfuscator with auxiliary inputs for point programs over $\zo^n$ that is $(s_{obf}, \epsilon_{obf})$-hard.  Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.  Then $H^{\hill}_{\epsilon', s_{obf}}( C | P ) \geq |C| - \beta$ for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
\end{theorem}

\noindent
We now prove $S$ cannot distinguish between $C$ and $C'$.  
Let $\mathcal{I}$ be the set of all indices in \defref{def:block guessable}.  Recall that $C'$ is a uniformly distributed codeword conditioned on agreeing with $C$ in all coordinates of $C_{\mathcal{I}^c}$.
\begin{lemma}
\label{lem:sim cannot distinguish}
$\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) \le (\ell-\beta) 2^{-(\alpha+1)}$.
\end{lemma}

\begin{proof}
\noindent It suffices to show that for any two codewords that agree on $\mathcal{I}^c$, the statistical distance is at most $2^{-(\alpha+1)}$.
\begin{lemma}
\label{lem:codewords in I close}
Let $c^*$ be true value encoded in $X$ and let $c'$ a codeword in $C'$.  Then, 
\[
\Delta( S^{\mathcal{O}_X(\cdot, \cdot)}(c^*), S^{\mathcal{O}_X(\cdot, \cdot)}(c')) \le ( \ell -\beta) 2^{-(\alpha+1)}.
\]
\end{lemma}
\begin{proof}
Recall that for all $i\in \mathcal{I}$, $\Hav(W_i | View(S))\geq \alpha$.  The only information about the correct value of $c_i^*$ is contained in the query responses.  When all responses are $0$ the view of $S$ is identical when presented with $c^*$ or $c'$.  We now show that for any value of $c^*$ all queries on $i \in \mathcal{I}$ return $0$ with probability $1-2^{-\alpha+1}$.  Suppose not, that is suppose, the probability of at least one nonzero response on index $i$ is $> 2^{-(\alpha+1)}$.  Since $w, w'$ are independent of $r_i$, the probability of this happening when $c^*_i = 1$ is at most $q/2^n$ or equivalently $2^{-n+\log q}$.  Thus, it must occur with probability:
\begin{align}
2^{-\alpha+1}&<\Pr[\text{non zero response location }i]\nonumber \\
 &= \Pr[c_i^* =1]\Pr[\text{non zero response location }i\wedge c_i^*=1]\nonumber \\&+ \Pr[c_i^*=0] \Pr[\text{non zero response location }i \wedge c_i^*=0]\nonumber \\
&\le 1\times 2^{-n+\log q} + 1\times  \Pr[\text{non zero response location }i \wedge c_i^*=0] \label{eq:ways to remove ent}
\end{align}
We now show that $n-\log q \geq \alpha$:
\begin{claim}
\label{cl:ent bounded away from n}
$n-\log q \geq \alpha$
\end{claim}
\begin{proof}
It suffices to show that there exists a simulator $S$ making $q$ queries such that the remaining entropy in that block is at most $n-\log q$.  Let $W_i$ be a distribution, consider $S$ that asks the $q$ most likely outcomes, the total probability of this block must be at least $2^{-n+\log q}$.  After these queries the remaining min-entropy is at most:
\begin{align*}
\Hav(W_i | View(S)) &\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1+ \Pr[\text{no }q_i=1]\times \Pr[\text{most likely outcome}|q_1,...,q_q]\right)\\
&\leq  -\log \left(\Pr[\text{some }q_i=1]\times 1\right)\\
&=-\log\left( 2^{-n+\log q} \right) = n-\log q
\end{align*}
This completes the proof of \clref{cl:ent bounded away from n}.
\end{proof}
\noindent
Rearranging terms in Equation~\ref{eq:ways to remove ent}, we have:
\begin{align*}
 \Pr[\text{non zero response location }i \wedge c_i=0] &>2^{-\alpha+1} - 2^{-(n-\log q)}=  2^{-\alpha}
 \end{align*}
 When there is a $1$ response and $c_i=0$ this means that there is no remaining min-entropy.  If this occurs with over $2^{-\alpha}$ probability this violates the block unguessability of $W$~(\defref{def:block guessable}).  By the union bound over the indices $i\in\mathcal{I}$ the total probability of a $1$ in $\mathcal{I}$ is at most $(\ell-\beta)2^{-\alpha+1}$. Thus, for all $c_1, c_2\in C| C_{\mathcal{I}^c}$ the statistical distance is at most $(\ell- \beta)2^{-\alpha+1}$.  This concludes the proof of \lemref{lem:codewords in I close}
\end{proof}
By averaging over all points in $C'$ we conclude that $\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) < (\ell -\beta)2^{-(\alpha+1)}$.  This completes the proof of \lemref{lem:sim cannot distinguish}.
\end{proof}

%The prior lemma implies that the $View$ does not increase the probability of any codeword by much.
%\begin{lemma}
%\label{lem:no codeword high prob}
%For all $c\in C|C_{\mathcal{I}^c}$, 
%\[
%\expe_{View(S)} \Pr[C=c | C_{\mathcal{I}^c} \wedge View(S)] \leq \Pr[C=c | C_{\mathcal{I}^c}]+2^{-(\alpha-1)}.
%\]
%\end{lemma}
%\begin{proof}
%We begin by noting there must exist some $c\in C|C_{\mathcal{I}^c}$ such that 
%\[
%\expe_{view\leftarrow View}\Pr[C = c | C_{\mathcal{I}^c}] \le \frac{1}{| C| C_{\mathcal{I}^c}|}.
%\]
%Otherwise the sum of the probabilities of $c\in C | C_{\mathcal{I}^c}$ will be greater than $1$.  Let $c_{min}$ be one such value.
%Let $c^*$ be an arbitrary $c^*$ in the support of $C|C_{\mathcal{I}^c}$.  Suppose that  
%\begin{align*}
%\expe_{view \leftarrow View(A^{\mathcal{O}_{(X_1,..., X_\ell)}})}\Pr[C=c^* | C_{\mathcal{I}^c} \wedge view ] &\geq \Pr[C=c^* | C_{\mathcal{I}^c} ]+ 2^{-(\alpha-1)} \\
%\end{align*}
%This means that the difference between the expected probability of $c_{min}$ and $c^*$ is at least $2^{-\alpha+1}$.  Thus, there is an unbounded distinguisher that can tell between the two cases, violating the statistical distance property of   \lemref{lem:codewords in I close}.  This is a contradiction and completes the proof.
%\end{proof}
%\begin{corollary}
%\label{cor:avg min after view}
%$\Hav(C| View(S))\geq \Hav(C | View (A) \wedge C_{\mathcal{I}^c}) \geq \min \{ \Hav(C | C_{\mathcal{I}^c}), \alpha-1\} -1= \min\{ |C| - |\mathcal{I}^c|, \alpha-1\} -1$.
%\end{corollary}
%\begin{proof}
%%Let $e$ be the exponent of the particular negligible value above~(note $e = \omega(1)$). 
%Taking the negative log of \lemref{lem:no codeword high prob} one has:
%\begin{align*}
%\Hav(C_i |  View(A^{\mathcal{O}_{(X_1,..., X_\ell)}(\cdot)}))
% &= \\
% -\log \left(\expe_{view \leftarrow View}\max_{c\in C|C_{\mathcal{I}^c}}\Pr[C =c | view \wedge C_{\mathcal{I}^c} ]  \right) &\geq -\log (\Pr[C=c^* | C_{\mathcal{I}^c} ]+ 2^{-\alpha+1}) \\
% &\geq \min \{-\log P_c, -\log 2^{-\alpha+1}\} -1\\
% &= \min \{ \Hav(C | C_{\mathcal{I}^c}), \alpha-1\}-1 
%\end{align*}
%\end{proof}

@@

\noindent
We now show that there must be a super-logarithmic jump early enough.
